### 2014-06-06 paper/body.tex
editing main contributions

Once one has general features from some layer of a \emph{base} network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \citep{donahue+jia-2013-arxiv}. The usual course is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second \emph{target} task. When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left frozen, meaning that they do not change during training on the new task. In cases where the target dataset is smaller than the base dataset, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the target dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the target dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch. We compare results from each of these two domains --- fine-tuned features or frozen features --- in a later section.

@@

\begin{enumerate}
\item We propose one way of answering the first question above through the degree to which features from one dataset transfer to another (Section~\ref{sec:definition}). We then train a large convnet on the ImageNet dataset and use our definition of generality to examine the general to specific transition (Section~\ref{sec:experiments}).
Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \cite{donahue+jia-2013-arxiv} but here we further characterize the general to specific transition, which yields the next three results.
\item We experimentally show that the difficulty in using transferred features can be decomposed into two separate issues: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers and the specificity of the features themselves. In different regions of the network, we show how different effects dominate (Section~\ref{sec:experiments_ab}).
\item We show how the transferability gap grows as the distance between base
task and target task increases, and we compare both types of transfer to using random filters, which we find not to work as well on the large ImageNet dataset as for smaller datasets, as reported by \cite{Jarrett-ICCV2009}.
\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better solutions, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
\end{enumerate}

>>>>

Once one has general features from some layer of a \emph{base} network trained on a dataset, a common trick is to repurpose the features, or \emph{transfer} them, to another task \citep{donahue+jia-2013-arxiv}. The usual course is to create a new network containing as its first $n$ layers the first $n$ layers of the base network, with the rest of the layers in the new network randomly initialized and trained toward the second \emph{target} task. When following this path, one can choose to backpropagate the errors from the new task into the base (copied) features to \emph{fine-tune} them to the new task, or they can be left \emph{frozen}, meaning that they do not change during training on the new task. In cases where the target dataset is smaller than the base dataset, fine-tuning the base features may result in overfitting, so the features are often left frozen. On the other hand, if the target dataset is large enough, the base features can be fine-tuned to the new task. Of course, if the target dataset is very large, there would be little need to transfer because the base filters could just be learned from scratch. We compare results from each of these two techniques --- fine-tuned features or frozen features --- below.

@@

\begin{enumerate}
\item We introduce a way to quantify the degree to which a particular layer is general or specific: how well features at a certain layer transfer from one dataset to another (Section~\ref{sec:definition}). We test this proposed measure on a large convnet trained on the ImageNet dataset. These experiments also reveal the transition from general to specific layers (Section~\ref{sec:experiments}).
Others have loosely addressed the question of generaltiy by showing how features from higher layers in a convnet can be transferred to new tasks \citep{donahue+jia-2013-arxiv}, but here we further characterize the general to specific transition, which yields the next three results.
\item We experimentally show two separate issues that cause performance declines from transferred features: optimization difficulties due to breaking co-adaptation between neurons on neighboring layers, and the specificity of the features themselves. We show how different effects dominate at different layers of the network (Section~\ref{sec:experiments_ab}).
\item We show how the transferability gap grows as the similarity between base
task and target task decreases. 
\item We compare both frozen and fine-tuning transfer to using random filters: we find that random filters do not work as well on the large ImageNet dataset as they have been reported to for smaller datasets \citep{Jarrett-ICCV2009}.
\item Finally, we find an interesting effect where fine-tuning filters from a different dataset can lead to better performance, even when the datasets are the same size and training time is identical (Section~\ref{sec:experiments_ab}).
\end{enumerate}
